---
title: "addr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{addr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## addr vectors in R

The `addr` package provides the `addr` R object, which stores standardized address tags, but acts like a usual vector in R:

```{r example}
library(addr)
```

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140"))
```

Under the hood, an `addr` vector keeps a record of the tagged and standardized address components so that they can be used with other functions. To inspect or use them directly:

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140")) |>
  as.data.frame()
```

or

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140")) |>
  as.character()
```

## addr matching

List all of the potentially matching `addr`s in a reference set of `addr`s with `addr_match()`. The code below matches input addresses to the reference set of all addresses in Hamilton County, OH included in the package:

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", 
    "5130 RAPID RUN RD CINCINNATI OHIO 45238",
    "5131 RAPID RUN RD CINCINNATI OHIO 45238"
)) |>
  addr_match(cagis_addr()$cagis_addr)
```

Use the matched addr vector to merge in address-specific data in the included `cagis_addr` object.

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "5130 RAPID RUN RD CINCINNATI OHIO 45238")) |>
  addr_match(cagis_addr()$cagis_addr, simplify = TRUE) |>
  tibble::enframe(name = "input_addr", value = "ca") |>
  dplyr::left_join(cagis_addr(), by = c("ca" = "cagis_addr"))
```

If exact matching fails, use matching to TIGER street range files from the US census:

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "5130 RAPID RUN RD CINCINNATI OHIO 45238")) |>
  addr_match_tiger_street_ranges()
```

Because the addresses are possibly located on more than one street range geography, use the `summarize` argument to return the centroid of each set of matched street ranges and then add TIGER/Line census block group identifers via geospatial intersection:

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "5130 RAPID RUN RD CINCINNATI OHIO 45238")) |>
  addr_match_tiger_street_ranges(county = "39061", summarize = "centroid") |>
  dplyr::bind_rows() |>
  dplyr::mutate(census_bg_id = s2_join_tiger_bg(s2::as_s2_cell(s2_geography)))
```

The above process is conducted, with default matching arguments, in the function `addr_match_geocode`, which requires a vector of reference s2 cell locations:  **As of now, this process only works with the `cagis_s2` available as below and for matching within Hamilton County, OH (36061) using 2022 TIGER street range files**

```{r}

# select one s2 cell at random from addresses with more than one parcel identifier and coordinates
cagis_s2 <-
   cagis_addr()$cagis_addr_data |>
   purrr::modify_if(\(.) length(.) > 0 && nrow(.) > 1, dplyr::slice_sample, n = 1) |>
   purrr::map_vec(purrr::pluck, "cagis_s2", .default = NA, .ptype = s2::s2_cell())
   
addr_match_geocode(x = voter_addresses()[1040:1100], 
                   ref_addr = cagis_addr()$cagis_addr,
				   ref_s2 = cagis_s2,
				   county = "39061",
				   year = "2022")
```
