---
title: "addr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{addr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(timeout = 360)
Sys.setenv("R_USER_CACHE_DIR" = tempfile())
```

## addr vectors in R

The `addr` package provides the `addr` R object, which stores standardized address tags, but acts like a usual vector in R:

```{r example}
library(addr)
```

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140"))
```

Under the hood, an `addr` vector keeps a record of the tagged and standardized address components so that they can be used with other functions. To inspect or use them directly:

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140")) |>
  as.data.frame()
```

or

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", "202 Riva Ridge Ct Cincinnati OH 45140")) |>
  as.character()
```

## addr matching

List all of the potentially matching `addr`s in a reference set of `addr`s with `addr_match()`.
The code below matches input addresses to addresses in the National Address Database subset for Hamilton County, OH included in the package (see `?nad_addr`):

```{r}
addr(c("3333 Burnet Ave Cincinnati OH 45229", 
    "5130 RAPID RUN RD CINCINNATI OHIO 45238",
    "5131 RAPID RUN RD CINCINNATI OHIO 45238"
)) |>
  addr_match(nad_addr()$nad_addr)
```
